### 2023-04-17 Notes/nonmonotone_project.tex
Wrote up double robustness. Modified simulations in Simulations/nonmonotone.R so that tables are reproducible.

\section*{Completed:}

@@

   However, we keep the same structure for the Stage 2 probabilities with:
   $p_{12} = \logistic(y_1)$ and $p_{21} = \logistic(y_2)$. The goal remains to
   estimate $\theta$. We continue to use the Oracle algorithm and the IPW-Oracle
   algorithm. Since we have nonmonotone MAR data, we use the ``Proposed''
   algorithm that is described on Slide 25 (Equation 12) of Dr. Kim's
   presentation. The response models and outcome models were estimated using
   logistic regression and OLS and correctly specified. This yields the
   following results:

    \input{Tables/nonmonocmar_t-5cy1y20.tex}
    \input{Tables/nonmonocmar_t0cy1y20.tex}
    \input{Tables/nonmonocmar_t5cy1y20.tex}

@@

    \input{Tables/nonmonocmar_t0cy1y20.1.tex}
    \input{Tables/nonmonocmar_t0cy1y20.5.tex}
    \input{Tables/nonmonocmar_t0cy1y20.9.tex}

@@

    \input{Tables/nmonocmar_t0cy1y20.tex}
    \input{Tables/nmonocmar_t0cy1y20.1.tex}
    \input{Tables/nmonocmar_t0cy1y20.5.tex}

@@

    Clearly, the proposed method is unbiased with a misspecified outcome model.
    When the response model is misspecified as in Simulation 1, the procedure
    still works.

@@

{\bf Commments from JK}
\begin{itemize}
    \item Three variables $(X, Y_1, Y_2)$ should be correlated. 
\end{itemize}

>>>>

\section*{Initial Simulations:}
% Tables generated from Simulations/nonmonotone.R

@@

   However, we keep the same structure for the Stage 2 probabilities with:
   $p_{12} = \logistic(y_1)$ and $p_{21} = \logistic(y_2)$. The goal remains to
   estimate $\theta$. We continue to use the Oracle algorithm and the IPW-Oracle
   algorithm. Since we have nonmonotone MAR data, we use the ``Proposed''
   algorithm that is described on Slide 25 (Equation 12) of Dr. Kim's
   presentation. The outcome models were estimated using
   logistic regression and OLS and correctly specified. The response model used
   the oracle estimates of the probabilites. This yields the
   following results:

    \input{Tables/nonmonosim1m-5.tex}
    \input{Tables/nonmonosim1m0.tex}
    \input{Tables/nonmonosim1m5.tex}

@@

    \input{Tables/nonmonosim2c0.1.tex}
    \input{Tables/nonmonosim2c0.5.tex}
    \input{Tables/nonmonosim2c0.9.tex}

@@

    \input{Tables/nonmonosim3c0.tex}
    \input{Tables/nonmonosim3c0.1.tex}
    \input{Tables/nonmonosim3c0.5.tex}

@@

    Thus, the proposed method is unbiased with a misspecified outcome model.
    We now show a simulation where the outcome model is correctly specified but
    the response model is not.

  \item \textbf{Simulation 4 with Nonmonotone MAR}:
    Continuing to test if the proposed algorithm is doubly robust, this
    simulation checks a misspecified response model. Instead of using oracle
    weights as in Simulation 3, we estimate the weights for the proposed method.
    The algorithms to which we compare still use the oracle weights.

    \input{Tables/nonmonosim4c0.tex}
    \input{Tables/nonmonosim4c0.1.tex}
    \input{Tables/nonmonosim4c0.5.tex}

    This is clear evidence that the proposed method is doubly robust.

@@

\section*{Full Nonmonotone Estimator}

\begin{itemize}
  \item
